Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-02-12 latex/comp_or.tex
Experimentation with dist from ramp door have started

>>>>

Let $\pi$ be a tour in the set of permutations of nodes.

Let $maxD$ be the distance from the last ramp pallet to the center of gravity.

Let $Q  = \{ a^{\pi(k_1)}, a^{\pi(k_2)}, \ldots, a^{\pi(k_{m})} \}$ be the set of consolidated items assembled on the set of $m$ pallets in node $\pi(k)$.

Let $Z^{\pi(k)}_{iq}$ be the set of decision variables that relates pallet $i$ to consolidated $q$ in node $\pi(k)$.

\begin{equation} \label{eq:distobj}
	\mbox{minimize} \sum_{i=1}^{m} \sum_{q=1}^{m} Z^{\pi(k)}_{iq} \times ( maxD - p_i.d) ,\ \mbox{{\bf if}}\ a^{\pi(k)}_q.to = \pi(k+1) \}
\end{equation}

\begin{equation} \label{eq:distcons}
	s.t.: \sum_{i=1}^{m} Z^{\pi(k)}_{iq} = 1;\ q \in \{1,2,\ldots,m\}
\end{equation}

\begin{equation} \label{eq:distpallets}
	s.t.: \sum_{q=1}^{m} Z^{\pi(k)}_{iq}=1;\ i \in \{1,2,\ldots,m\}
\end{equation}

\begin{equation} \label{eq:distpalletw}
	p_i.w = 140 + a^{\pi(k)}_q.w ;\ i \in \{1,2,\ldots,m\};\ q \in \{1,2,\ldots,m\}
\end{equation}

\begin{equation} \label{eq:disttorque}
	s.t.:\ | \sum\ p_i.d * p_i.w\ | \leq maxW \times limit^{CG}_{long} ;\ i \in \{1,2,\ldots,m\}
\end{equation}

Equation \ref{eq:distobj} minimizes the sum of distances of the consolidated in node $\pi(k)$ destined to the next node $\pi(k+1)$; Equation \ref{eq:distcons} states that each consolidated will be assigned to exactly one pallet; Equation \ref{eq:distpallets} states that each pallet will receive one consolidated; Equation \ref{eq:distpalletw} calculates the total weight of each pallet; and Equation \ref{eq:disttorque} guarantees that the torque limit will not be exceeded.

As the number of pallets was small for an integer program solver, the increased time was negligible.

Columns {\bf Before} and {\bf After} on Table \ref{tab:distRampDoor} refer to the application of the integer programming solver according to equations \ref{eq:distobj} to \ref{eq:disttorque}.

\begin{table}[H]
\centering
\caption{Distance from ramp door minimization}  \label{tab:distRampDoor}
\footnotesize
%\scriptsize
\begin{tabular}{cccc}
\toprule

{\bf Surplus} & {\bf Scenario} & {\bf Before (m)} & {\bf After (m)} \\
\midrule
\multirow{6}{*}{$1.2$}&1 & 7.07 & 7.07 \\
&                     2 & 41.23 & 37.52 \\
&                     3 & 24.03 & 24.64 \\
&                     4 & 26.84 & After \\
&                     5 & Before & After \\
&                     6 & Before & After \\
\midrule
\multirow{6}{*}{$1.5$}&1 & 7.07 & 7.07 \\
&                     2 & 41.23 & 37.52 \\
&                     3 & 24.03 & 24.64 \\
&                     4 & 26.84 & After \\
&                     5 & Before & After \\
&                     6 & Before & After \\
\midrule
\multirow{6}{*}{$2.0$}&1 & 7.07 & 7.07 \\
&                     2 & 41.23 & 37.52 \\
&                     3 & 24.03 & 24.64 \\
&                     4 & 26.84 & After \\
&                     5 & Before & After \\
&                     6 & Before & After \\
\midrule
&                     {\bf Average} & Before & After \\
\bottomrule	
\end{tabular}
%\textsuperscript{asdf sd .}	
\normalsize
\end{table}
